|

### 2022-12-28 paper.Rmd
autogit

```{bash ipythonRunner}
# Find all *.ipynb files in subdirectories recursively
for file in $(find . -type f -name "*.ipynb"); do
  # Execute the IPython notebook file using the jupyter nbconvert command
  jupyter nbconvert --execute "${file}"
done
```

@@

The strategy of pre-training artificial neural networks is based on the idea of transfer learning. 
Transfer learning in the field of machine learning aims at retaining previously learned knowledge from one task to re-use it for another task [@HAN2021225] [@survey_transfer_learning]. Transfer learning traditionally follows a two phase approach:

@@

where source task and target task are usually similar but may differ in their feature space and the distribution of training data [@survey_transfer_learning].
One of the main motivations for using transfer learning in real world machine learning tasks is the ability to reduce the need for large amounts of training data which can often be unavailable or too expensive to collect.

Pre-Training is a commonly used strategy in deep architectures that has been shown to improve both the optimization process itself as well as the generalization behavior if compared to randomly initialized parameters [@pmlr-v5-erhan09a].

>>>>

```{bash ipythonRunner, include=FALSE}

# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

# Find all *.ipynb files in subdirectories of EXPDIR, including sub-sub directories, etc., but exclude files that contain the word "checkpoint" in the filename
for file in $(find "$EXPDIR" -type f -name "*.ipynb" ! -name "*checkpoint*"); do
  # Change to the directory containing the IPython notebook file
  cd "$(dirname "$file")"
  # Execute the IPython notebook file using the jupyter nbconvert command
  ipython "$(basename "$file")"
done

@@

Pre-Training describes the concept of initially training a neural network on a large dataset before using it to solve a more specific task. It is a commonly used strategy in deep architectures that has been shown to improve both the optimization process itself as well as the generalization behavior if compared to the standard approach of using randomly initialized parameters [@pmlr-v5-erhan09a].

The strategy of pre-training artificial neural networks is based on the idea of transfer learning that aims at retaining previously learned knowledge from one task to re-use it for another task [@HAN2021225] [@survey_transfer_learning]. Transfer learning traditionally follows a two phase approach:

@@

where source task and target task are usually similar but may differ in their feature space and the distribution of training data [@survey_transfer_learning].

Some of the main motivations for using pre-training is the ability to reduce the need for large amounts of training data which can often be unavailable or too expensive to collect as well as an improved performance by either reducing the computational effort that is necessary to train a model to solve a specific task or by improving the models generalisation ability.
